Bumble bee foraging bias

### 2021-01-15 code/visitation_bias.Rmd
oh yeah

---
title: "visitation_bias"
author: "Doug Sponsler"
date: "12/14/2020"
output: html_document
---
# Preparations
## Packages 
```{r, warning=FALSE, include=FALSE, echo = FALSE}
library(bipartite)
library(mgcv)
library(mgcViz)
library(brms)
library(lme4)
library(bayesplot)
library(vegan)
library(tidyverse)
library(lubridate)
library(tidymodels)
```

@@

# This model includes a global interaction term for yday and elevation, with a varying intercept for bb.sp and a varying slow for elev | bb.sp. I think this should give me all the estimation I'm interested in. It's tricky to make it converge, though.
brm.plantsp11 <- brm(dprime ~ yday * elev + (1 + elev | bb.sp), 
                  control = list(max_treedepth = 10),
                  cores = 4,
                  iter = 4000,
                  #family = "skew_normal",
                  file = "../output/brm_plantsp11",
                  data = filter(bias, criterion ==  "plant.sp"))

summary(brm.plantsp11)
prior_summary(brm.plantsp11)
plot(brm.plantsp11)
parnames(brm.plantsp11)
mcmc_plot(brm.plantsp11, pars = c("^r_"))
mcmc_plot(brm.plantsp11, pars = c("elev"))
mcmc_plot(brm.plantsp11, pars = c("^b_"))
mcmc_plot(brm.plantsp11)
conditional_effects(brm.plantsp11)
pp_check(brm.plantsp11)
bayes_R2(brm.plantsp11)
hypothesis(brm.plantsp11, "b_elev = 0", class = NULL)

# Alternatively, we can drop the varying slope term to simplify the model a bit. Still doesn't quite converge.
brm.plantsp1 <- brm(dprime ~ yday * elev + (1 | bb.sp), 
                  control = list(max_treedepth = 10),
                  cores = 4,
                  iter = 2000,
                  file = "../output/brm_plantsp1",
                  data = filter(bias, criterion ==  "plant.sp"))

summary(brm.plantsp1)
prior_summary(brm.plantsp1)
plot(brm.plantsp1)
parnames(brm.plantsp1)
mcmc_plot(brm.plantsp1, pars = c("^r_"))
mcmc_plot(brm.plantsp1, pars = c("elev"))
mcmc_plot(brm.plantsp1, pars = c("^b_"))
mcmc_plot(brm.plantsp1)
conditional_effects(brm.plantsp1)
pp_check(brm.plantsp1)
bayes_R2(brm.plantsp1)
hypothesis(brm.plantsp1, "b_elev = 0", class = NULL)

# We can simplify the model still more by dropping the yday*elev interaction term. Now it converges. But I think the takeaway is that neither elevation noy yday give us a clear signal with respect  to dprime.
brm.plantsp2 <- brm(dprime ~ yday + elev + (1 | bb.sp), 
                  control = list(max_treedepth = 10),
                  cores = 4,
                  iter = 2000,
                  file = "../output/brm_plantsp2",
                  data = filter(bias, criterion ==  "plant.sp"))

summary(brm.plantsp2)
prior_summary(brm.plantsp2)
plot(brm.plantsp2)
parnames(brm.plantsp2)
mcmc_plot(brm.plantsp2, pars = c("^r_"))
mcmc_plot(brm.plantsp2, pars = c("elev"))
mcmc_plot(brm.plantsp2, pars = c("^b_"))
mcmc_plot(brm.plantsp2)
conditional_effects(brm.plantsp2)
pp_check(brm.plantsp2)
bayes_R2(brm.plantsp2)
hypothesis(brm.plantsp2, "b_elev = 0", class = NULL)

@@

# I guess the message here is that both bb.sp and site contribute to the variation of dprime, but site more so. Biologically, I think the meaning of prime variation by site is that some sites have greater relative abundance of *attractive* flora than others. A site with loads of something that is never visited and a little bit of clover will yield a high dprime, while a site with a high abundance of attractive floral would yield a low dprime.
mcmc_plot(brm.plantsp0, pars = c("^r_"))
mcmc_plot(brm.plantsp0, pars = c("^r_bb.sp")) 
ggsave("../output/brm.plantsp0_plot1.png")
mcmc_plot(brm.plantsp0, pars = c("^b_"))
pp_check(brm.plantsp0)
bayes_R2(brm.plantsp0)

# Another option would be to drop just elevation from the model. This runs clean. Doesn't explain much more variance than the simpler model, though.
brm.plantsp00 <- brm(dprime ~ yday + (1 | bb.sp) + (1 | site),
                  control = list(max_treedepth = 10),
                  cores = 4,
                  iter = 2000,
                  file = "../output/brm_plantsp00",
                  data = filter(bias, criterion ==  "plant.sp"))

summary(brm.plantsp00)
plot(brm.plantsp00)
parnames(brm.plantsp00)
mcmc_plot(brm.plantsp00, pars = c("^r_"))
mcmc_plot(brm.plantsp00, pars = c("^b_"))
conditional_effects(brm.plantsp00)
pp_check(brm.plantsp00)
bayes_R2(brm.plantsp00)

# Let's do a formal comparison of the last three models
waic(brm.plantsp2, brm.plantsp0, brm.plantsp00)

# The one including yday is a *slight* winner, but the margin is so small as to be meaningless. I think the simplest model is the one we want (brm.plantsp0).

# Let's try the same model now, but for ktype.
brm.ktype0 <- brm(dprime ~ 1 + (1 | bb.sp) + (1 | site),
                  control = list(max_treedepth = 10),
                  cores = 4,
                  iter = 2000,
                  family = "skew_normal",
                  file = "../output/brm_ktype0",
                  data = filter(bias, criterion ==  "ktype"))

summary(brm.ktype0)
plot(brm.ktype0)
parnames(brm.ktype0)
mcmc_plot(brm.ktype0, pars = c("^r_"))
mcmc_plot(brm.ktype0, pars = c("^b_"))
conditional_effects(brm.ktype0)
pp_check(brm.ktype0)
bayes_R2(brm.ktype0)
```

@@

## 2.3 Calculate bias per plant speces/ktype/family
```{r}
representation <- biaseval_group(visit_cover, plant.sp) %>%
  rename(plant.sp = criterion) %>%
  left_join(site_data) %>%
  left_join(fl_traits) %>%
  mutate(k.type.ss = factor(k.type.ss)) %>%
  select(site, date, elev.mean, yday, bb.sp, plant.sp, k.type.ss, 
         prop.visits, prop.flower.cover, bias, visits, 
         flower.cover, plant.genus, plant.family) %>%
  left_join(bb_traits)

@@

## 2.5 Multi-level models
```{r}
# The tons of zeros are due to the lots of plant species that were present at very low abundance and received few or zero visits. 
ggplot(representation, aes(k.type.ss, bias)) +
  geom_violin()

ggplot(representation, aes(k.type.ss, bias)) +
  geom_boxplot()

ggplot(representation, aes(bias)) +
  geom_histogram() +
  facet_wrap(~k.type.ss)

ggplot(filter(representation, abs(bias) > 0.1), aes(bias)) +
  geom_histogram() +
  facet_wrap(~k.type.ss)

ggplot(filter(representation, prop.flower.cover > 0.05), aes(k.type.ss, bias)) +
  geom_boxplot()

ggplot(representation, aes(prop.flower.cover, prop.visits)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_wrap(~k.type.ss)

brm_representation0 <- brm(bias ~ 1 + (1 | k.type.ss) + (1 | site),
                 control = list(max_treedepth = 10),
                 cores = 4,
                 chains = 4,
                 iter = 2000,
                 file = "../output/brm_representation0",
                 data = representation)

summary(brm_representation0)
plot(brm_representation0)
parnames(brm_representation0)
mcmc_plot(brm_representation0, pars = c("^r_"))
#mcmc_plot(representation.ktype0, pars = c("elev"))
mcmc_plot(brm_representation0, pars = c("^b_"))
mcmc_plot(brm_representation0)
#conditional_effects(representation.ktype0)
pp_check(brm_representation0)
bayes_R2(brm_representation0)

brm_representation1 <- brm(bias ~ pbl.w + (1 + pbl.w | k.type.ss) + (1 | bb.sp),
                 control = list(max_treedepth = 10),
                 cores = 4,
                 chains = 4,
                 iter = 2000,
                 file = "../output/brm_representation1",
                 data = representation)

summary(brm_representation1)
plot(brm_representation1)
parnames(brm_representation1)
mcmc_plot(brm_representation1, pars = c("^r_"))
#mcmc_plot(representation.ktype1, pars = c("elev"))
mcmc_plot(brm_representation1, pars = c("^b_"))
mcmc_plot(brm_representation1)
#conditional_effects(representation.ktype1)
pp_check(brm_representation1)
bayes_R2(brm_representation1)

hypothesis(representation.ktype1, "r_group[5,Intercept] = r_group[6,Intercept]", class = "")
hypothesis(representation.ktype1, "r_group[1,Intercept] = r_group[0,Intercept]", class = "")

# One interesting way to think about bias is to focus on the slope of prop.visits ~ prop.flower.cover. 
# We could analyze this with a varying slope model

# Binomial ggplot smoother
binomial_smooth <- function(...) {
  geom_smooth(method = "glm", method.args = list(family = "quasibinomial"), se = FALSE, ...)
}

ggplot(representation, aes(sqrt(prop.flower.cover), sqrt(prop.visits))) +
  geom_point() +
  #geom_smooth(method = "lm") +
  #binomial_smooth(formula = y ~ splines::ns(x, 3)) +
  geom_smooth() +
  #geom_smooth(method = "glm", method.args = list(family = "binomial")) +
  facet_grid(k.type.ss~bb.sp)

brm_representation3 <- brm(prop.visits ~ prop.flower.cover + (1 + prop.flower.cover | k.type.ss),
                 control = list(max_treedepth = 10),
                 #cores = 4,
                 cores = 2,
                 chains = 2,
                 #iter = 2000,
                 iter = 1000,
                 file = "./output/brm_representation3",
                 data = representation)

lmer_representation3 <- lmer(prop.visits ~ log(prop.flower.cover) + (1 + log(prop.flower.cover) | k.type.ss),
                             data = representation)

summary(lmer_representation3)
plot(lmer_representation3)

# Can we explain anything with tongue length

ggplot(filter(representation, bb.sp != "gers" & abs(bias) >= 0.1), aes(pbl.w, bias)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_wrap(~k.type.ss)

lm_pbl <- lmer(bias ~ pbl.w + (1 + pbl.w | k.type.ss) + (1 | bb.sp),
               data = representation)

summary(lm_pbl)
```

@@

@@

>>>>

---
title: "visitation_bias"
author: "Doug Sponsler"
date: "12/14/2020"
output: html_document
---
# Preparations
## Packages 
```{r, warning=FALSE, include=FALSE, echo = FALSE}
library(bipartite)
library(brms)
library(lme4)
library(sjPlot)
library(DHARMa)
library(bayesplot)
library(vegan)
library(tidyverse)
library(lubridate)
library(tidymodels)
```

@@

# # This model includes a global interaction term for yday and elevation, with a varying intercept for bb.sp and a varying slow for elev | bb.sp. I think this should give me all the estimation I'm interested in. It's tricky to make it converge, though.
# brm.plantsp11 <- brm(dprime ~ yday * elev + (1 + elev | bb.sp), 
#                   control = list(max_treedepth = 10),
#                   cores = 4,
#                   iter = 4000,
#                   #family = "skew_normal",
#                   file = "../output/brm_plantsp11",
#                   data = filter(bias, criterion ==  "plant.sp"))
# 
# summary(brm.plantsp11)
# prior_summary(brm.plantsp11)
# plot(brm.plantsp11)
# parnames(brm.plantsp11)
# mcmc_plot(brm.plantsp11, pars = c("^r_"))
# mcmc_plot(brm.plantsp11, pars = c("elev"))
# mcmc_plot(brm.plantsp11, pars = c("^b_"))
# mcmc_plot(brm.plantsp11)
# conditional_effects(brm.plantsp11)
# pp_check(brm.plantsp11)
# bayes_R2(brm.plantsp11)
# hypothesis(brm.plantsp11, "b_elev = 0", class = NULL)
# 
# # Alternatively, we can drop the varying slope term to simplify the model a bit. Still doesn't quite converge.
# brm.plantsp1 <- brm(dprime ~ yday * elev + (1 | bb.sp), 
#                   control = list(max_treedepth = 10),
#                   cores = 4,
#                   iter = 2000,
#                   file = "../output/brm_plantsp1",
#                   data = filter(bias, criterion ==  "plant.sp"))
# 
# summary(brm.plantsp1)
# prior_summary(brm.plantsp1)
# plot(brm.plantsp1)
# parnames(brm.plantsp1)
# mcmc_plot(brm.plantsp1, pars = c("^r_"))
# mcmc_plot(brm.plantsp1, pars = c("elev"))
# mcmc_plot(brm.plantsp1, pars = c("^b_"))
# mcmc_plot(brm.plantsp1)
# conditional_effects(brm.plantsp1)
# pp_check(brm.plantsp1)
# bayes_R2(brm.plantsp1)
# hypothesis(brm.plantsp1, "b_elev = 0", class = NULL)
# 
# # We can simplify the model still more by dropping the yday*elev interaction term. Now it converges. But I think the takeaway is that neither elevation noy yday give us a clear signal with respect  to dprime.
# brm.plantsp2 <- brm(dprime ~ yday + elev + (1 | bb.sp), 
#                   control = list(max_treedepth = 10),
#                   cores = 4,
#                   iter = 2000,
#                   file = "../output/brm_plantsp2",
#                   data = filter(bias, criterion ==  "plant.sp"))
# 
# summary(brm.plantsp2)
# prior_summary(brm.plantsp2)
# plot(brm.plantsp2)
# parnames(brm.plantsp2)
# mcmc_plot(brm.plantsp2, pars = c("^r_"))
# mcmc_plot(brm.plantsp2, pars = c("elev"))
# mcmc_plot(brm.plantsp2, pars = c("^b_"))
# mcmc_plot(brm.plantsp2)
# conditional_effects(brm.plantsp2)
# pp_check(brm.plantsp2)
# bayes_R2(brm.plantsp2)
# hypothesis(brm.plantsp2, "b_elev = 0", class = NULL)

@@

# Out of curiosity, let's see what we get from the lme4 approach to the same model; we can use this as a sanity check of sorts. If the results of lme4 differ dramatically from those of brms, we might wonder why.
lme4.plantsp0 <- lmer(dprime ~ 1 + (1 | bb.sp) + (1 | site),
                      data = filter(bias, criterion ==  "plant.sp"))

summary(lme4.plantsp0)
#plot_model(lme4.plantsp0, type = "pred")
plot_model(lme4.plantsp0, type = "re")

lme4.plantsp1 <- lmer(dprime ~ elev * yday + (1 | bb.sp) + (1 | site),
                      data = filter(bias, criterion ==  "plant.sp"))

summary(lme4.plantsp1)
plot_model(lme4.plantsp1, type = "pred")
plot_model(lme4.plantsp1, type = "pred", terms = c("yday", "elev"))
plot_model(lme4.plantsp1, type = "re")

AIC(lme4.plantsp1)
AIC(lme4.plantsp0)

# 
# # I guess the message here is that both bb.sp and site contribute to the variation of dprime, but site more so. Biologically, I think the meaning of prime variation by site is that some sites have greater relative abundance of *attractive* flora than others. A site with loads of something that is never visited and a little bit of clover will yield a high dprime, while a site with a high abundance of attractive floral would yield a low dprime.
# mcmc_plot(brm.plantsp0, pars = c("^r_"))
# mcmc_plot(brm.plantsp0, pars = c("^r_bb.sp")) 
# ggsave("../output/brm.plantsp0_plot1.png")
# mcmc_plot(brm.plantsp0, pars = c("^b_"))
# pp_check(brm.plantsp0)
# bayes_R2(brm.plantsp0)
# 
# # Another option would be to drop just elevation from the model. This runs clean. Doesn't explain much more variance than the simpler model, though.
# brm.plantsp00 <- brm(dprime ~ yday + (1 | bb.sp) + (1 | site),
#                   control = list(max_treedepth = 10),
#                   cores = 4,
#                   iter = 2000,
#                   file = "../output/brm_plantsp00",
#                   data = filter(bias, criterion ==  "plant.sp"))
# 
# summary(brm.plantsp00)
# plot(brm.plantsp00)
# parnames(brm.plantsp00)
# mcmc_plot(brm.plantsp00, pars = c("^r_"))
# mcmc_plot(brm.plantsp00, pars = c("^b_"))
# conditional_effects(brm.plantsp00)
# pp_check(brm.plantsp00)
# bayes_R2(brm.plantsp00)
# 
# # Let's do a formal comparison of the last three models
# waic(brm.plantsp2, brm.plantsp0, brm.plantsp00)
# 
# # The one including yday is a *slight* winner, but the margin is so small as to be meaningless. I think the simplest model is the one we want (brm.plantsp0).
# 
# # Let's try the same model now, but for ktype.
# brm.ktype0 <- brm(dprime ~ 1 + (1 | bb.sp) + (1 | site),
#                   control = list(max_treedepth = 10),
#                   cores = 4,
#                   iter = 2000,
#                   family = "skew_normal",
#                   file = "../output/brm_ktype0",
#                   data = filter(bias, criterion ==  "ktype"))
# 
# summary(brm.ktype0)
# plot(brm.ktype0)
# parnames(brm.ktype0)
# mcmc_plot(brm.ktype0, pars = c("^r_"))
# mcmc_plot(brm.ktype0, pars = c("^b_"))
# conditional_effects(brm.ktype0)
# pp_check(brm.ktype0)
# bayes_R2(brm.ktype0)
```

@@

## 2.3 Calculate visitation probability per plant speces/ktype/family
```{r}
visit_prob <- visit_cover %>%
  group_by(site, date, bb.sp, plant.sp) %>%
  summarize(flower.cover = sum(flower.cover), # get raw flower cover and visits by group
            visits = sum(visits)) %>%
  group_by(site, date) %>%
  mutate(prop.flower.cover = flower.cover/sum(flower.cover), # get proportional flower cover and visits by group
         prop.visits = visits/sum(visits),
         visits.bin = factor(if_else(visits > 0, 1, 0))) %>%
  group_by(site, date, bb.sp) %>%
  mutate(bb.sp.abund = sum(visits)) %>%
  left_join(fl_traits) %>%
  left_join(bb_traits) %>%
  select(site, date, bb.sp, plant.sp, visits.bin, prop.flower.cover, k.type.ss, bb.sp.abund, pbl.w.class2) %>%
  mutate(k.type.ss = factor(k.type.ss))

# Pooled across BB spp
visit_prob_pooled <- visit_cover %>%
  group_by(site, date, plant.sp) %>%
  summarize(flower.cover = sum(flower.cover), # get raw floer cover and visits by group
            visits = sum(visits)) %>%
  group_by(site, date) %>%
  mutate(prop.flower.cover = flower.cover/sum(flower.cover), # get proportional flower cover and visits by group
         prop.visits = visits/sum(visits),
         bb.abund = sum(visits),
         visits.bin = factor(if_else(visits > 0, 1, 0))) %>%
  mutate(yday = yday(date)) %>%
  left_join(fl_traits) %>%
  mutate(k.type.ss = factor(k.type.ss))

@@

## 2.5 Multi-level models
My approach will be to fit models using both brms and lme4, partly as a learning exercise, partly to enable quicker model development, partly as a sanity check / back-up plan.

### Preliminary visualization
The tons of zeros are due to the lots of plant species that were present at very low abundance and received few or zero visits. This might not be ideal. We could opt for one of our alternative bias measure, like fold change, which all give something like a poisson distribution, but I don't know if this would be an improvement. We could also filter our data to include only plants that were above some threshold of relative abundance, say, 1%.
```{r}
# Bias
ggplot(representation, aes(k.type.ss, bias)) +
  geom_violin()

# Bias.fold
ggplot(representation, aes(k.type.ss, bias.fold)) +
  geom_violin()

# Bias.exp
ggplot(representation, aes(k.type.ss, bias.exp)) +
  geom_violin()

# Bias.bin
ggplot(representation, aes(k.type.ss, fill = bias.bin)) +
  geom_bar()

# Visits.bin
ggplot(representation, aes(k.type.ss, fill = visits.bin)) +
  geom_bar()

ggplot(visit_prob_pooled, aes(k.type.ss, fill = visits.bin)) +
  geom_bar(position = "fill")

# Bias filtered
ggplot(filter(representation, prop.flower.cover >= 0.05), aes(k.type.ss, bias)) +
  geom_violin()

ggplot(filter(representation, visits > 0), aes(k.type.ss, bias)) +
  geom_violin()

# Visits.bin filtered
ggplot(filter(representation, prop.flower.cover >= 0.05), aes(k.type.ss, fill = visits.bin)) +
  geom_bar()
```

### lme4 models
We will drop ktypes 9 and 10 from these models since both are vanishingly rare
```{r}
# This model does not parse by tongue length
glmer_vp00 <- glmer(visits.bin ~ prop.flower.cover + bb.sp.abund + (1 | k.type.ss) + (1 | site),
                    family  = "binomial",
                    data = filter(visit_prob, !k.type.ss %in% c("9", "10")))

plot_model(glmer_vp00, type = "pred")
plot_model(glmer_vp00, type = "re")

# This model does 
glmer_vp01 <- glmer(visits.bin ~ prop.flower.cover + bb.sp.abund + (1 | k.type.ss:pbl.w.class2) + (1 | site),
                    family  = "binomial",
                    data = filter(visit_prob, !k.type.ss %in% c("9", "10")))

plot_model(glmer_vp01, type = "pred")
plot_model(glmer_vp01, type = "re")
```

### brms models
```{r}
# This model does not parse by tongue length
brm_representation00 <- brm(visits.bin ~ prop.flower.cover + bb.sp.abund + (1 | k.type.ss) + (1 | site),
                            family = "bernoulli",
                            file = "../output/brm_vp00",
                            chains = 4,
                            cores = 4,
                            iter = 2000,
                            data = filter(visit_prob, !k.type.ss %in% c("9", "10")))

summary(brm_representation00)
prior_summary(brm_representation00)
parnames(brm_representation00)
mcmc_plot(brm_representation00, pars = c("^r_k"))
mcmc_plot(brm_representation00, pars = c("elev"))
mcmc_plot(brm_representation00, pars = c("^b_"))
mcmc_plot(brm_representation00)
conditional_effects(brm_representation00)
pp_check(brm_representation00)
bayes_R2(brm_representation00)

hypothesis(brm_representation00, "r_k.type.ss[0,Intercept] = r_k.type.ss[1,Intercept]", class = NULL)
hypothesis(brm_representation00, "r_k.type.ss[1,Intercept] = r_k.type.ss[2,Intercept]", class = NULL)
hypothesis(brm_representation00, "r_k.type.ss[6,Intercept] = r_k.type.ss[5,Intercept]", class = NULL)
hypothesis(brm_representation00, "r_k.type.ss[6,Intercept] = r_k.type.ss[5,Intercept]", class = NULL)
hypothesis(brm_representation00, "r_k.type.ss[6,Intercept] = r_k.type.ss[5,Intercept]", class = NULL)

# This model does
brm_representation01 <- brm(visits.bin ~ prop.flower.cover + bb.sp.abund + (1 | k.type.ss:pbl.w.class2) + (1 | site),
                            family = "bernoulli",
                            file = "../output/brm_vp01",
                            chains = 4,
                            cores = 4,
                            iter = 2000,
                            data = filter(visit_prob, !k.type.ss %in% c("9", "10")))

```

@@

rep_matrix.ktype2 <- representation %>%
  group_by(bb.sp, k.type.ss) %>%
  summarize(visit.bin = mean(bias)) %>%
  pivot_wider(values_from = visit.bin, names_from = k.type.ss, values_fill = 0) %>%
  column_to_rownames("bb.sp")

@@

pca.ktype <- rda(rep_matrix.ktype2)
#ef.ktype <- envfit(pca.ktype ~ pbl.w.class, data = traits)
#os.ktype <- ordisurf(pca.ktype ~ pbl.w.class, data = traits)
ef.ktype <- envfit(pca.ktype ~ pbl.w, data = traits)
os.ktype <- ordisurf(pca.ktype ~ pbl.w, data = traits)
plot(pca.ktype, type = "t")
plot(ef.ktype, add = TRUE)
plot(os.ktype)
```

### 2021-01-15 writing/manuscript_v4.Rmd
oh yeah

# Introduction

@@

# Methods

## Field sampling

@@

## Data analysis

@@

@@

# Results
## Cumulative bias across species and sites
```{r}
knitr::include_graphics("../output/brm.plantsp0_plot1.png")
```

## Parsing bias by floral morphotype [representation ~ 1 + (1 + ktype) + (1 + site)]

## Linking morphological bias to species' traits [bias ordination w/ tongue length]

##

# Discussion

@@

# References

>>>>

# 1. Introduction

@@

# 2. Methods

## 2.1 Field sampling

@@

## 2.2. Data analysis

@@

### 2.2.1 Modeling cumulative bias

@@

#### 2.2.2.1.1 Model 1: dprime ~

### 2.2.2 Modeling visitation probability as a function of floral morphotype and bumble bee tongue length

#### 2.2.2.1 Model 2: visits.bin ~ prop.flower.cover + bb.sp.abund + (1 | k.type.ss) + (1 | site)

#### 2.2.2.2 Model 3: visits.bin ~ prop.flower.cover + bb.sp.abund + (1 | k.type.ss:pbl.w.class2) + (1 | site)

#### 2.2.2.3 Model 4: Ordination with post-hoc fitting of tongue-length

### 2.2.3 Modeling the relationship between bias and niche relationships 
<!-- I might try to include a plant-centric analysis, too, to see how bias relates to potential competition between plants for BB pollinators. I think it is true to say that if floral resources are not limiting for bees, bee visitation is limiting for flora. -->

#### Model 5: niche_overlap ~ dprime

#### Model 6: Ordination of diet

# 3. Results
## 3.1 Model 1
```{r}
knitr::include_graphics("../output/brm.plantsp0_plot1.png")
```

## 3.2 Model 2

## 3.3. Model 3

## 3.4 Model 4

## 3.5 Model 5

## 3.6 Model 6

# 4. Discussion

## 4.1 The phenomenon of bias: Cumulative bias and variation across species

## 4.2 The mechanism of bias: Explaining bias by the interaction of flower and bumble bee morphology

## 4.3 The outcome of bias: Linking bias to niche relationships

@@

# 5. References
